Consistency scores in text data

### 2020-07-09 outputs/documents/paper.Rmd
write-ups updated, WIP
Add abstract.

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: pdflatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
biblio-style: apalike
title: "Consistency scores in text data"
thanks: "Our code and datasets are available at: X. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Ke-Li Chiu
  affiliation: University of Toronto  
abstract: "..."
keywords: "..."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
endnote: no
graphics: yes
---

@@

By including the $n$ into the previous conditional probability to be 
Pr($w_{k}$ | $w^{k-1}_{1}$)

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: pdflatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
biblio-style: apalike
title: "Consistency scores in text data"
thanks: "Our code and datasets are available at: X. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Ke-Li Chiu
  affiliation: University of Toronto  
abstract: "In this paper we use GPT-3 to clean the text from PDFs by comparing the original text with the generated text. We also introduce the notion of a consistency score, which refers to the proporation of text that is unchanged by the model, and is used to monitor changes during an iterative cleaning process. We illustrate our process on text from the Canadian Hansard and develop a Shiny application and R package to make our procedure easier for others to use."
keywords: "..."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
endnote: no
graphics: yes
---

@@

[Statistic notation of n-gram?]

[Character-level n-gram?]
